### 2012-03-27 intention motor representation with corrado sinigaglia/intention and motor action.ppr.r1.tex
after PPR resubmit (first revision)

\def \papersize {a4paper}

@@

\def \ititle {Intention and motor representation in explaining action}
\def \isubtitle {}
\def \iauthor {S. Butterfill* \& C. Sinigaglia**
\\ 
**Department of Philosophy, University of Warwick
\\ 
***Dipartimento di Filosofia, Università degli Studi di Milano}
\def \iemail{s.butterfill@warwick.ac.uk}
%\date{}

\input{$HOME/Documents/submissions/preamble_steve_paper2}
%\author{}
%\date{}

%\setromanfont[Mapping=tex-text]{Sabon LT Std}

@@

\begin{abstract}
Are there distinctive roles for intention and motor representation in explaining the purposiveness of action? Standard accounts of action assign a role to intention but are silent on motor representation. The temptation is to suppose that nothing need be said here because motor representation is either only an enabling condition for purposive action or else merely a variety of intention. This paper provides reasons for resisting temptation. Some motor representations, like intentions, coordinate actions in virtue of representing outcomes; but, unlike intentions, motor representations cannot feature as premises or conclusions in practical reasoning.  This implies that motor representation has a distinctive role in explaining the purposiveness of action. It also gives rise to a problem: were the roles of intention and motor representation entirely independent, this would impair effective action. Resisting temptation therefore requires explaining how intentions interlock with motor representations. The solution, we argue, is to recognise that the contents of intention can be partially determined by the contents of motor representations. Understanding this content-determining relation enables better understanding how intentions are related to actions.
\end{abstract}

@@

What is the relation between a purposive action and the outcome or outcomes to which it is directed? The standard way of answering this question appeals to intention, a propositional attitude which plays a characteristic role in planning and coordinating action, is linked to practical reasoning and is subject to characteristic norms (\citealp{Bratman:1987xw}).  On the standard view, an action is directed to an outcome in virtue of the action's being appropriately related to an intention which represents this outcome or some related outcome. As this view is usually expounded, the relation between actions and outcomes to which they are directed is treated as largely independent of the motor processes and representations underpinning action execution. Motor representations are usually considered either as philosophically irrelevant enabling conditions, or else as merely filling in additional details of the basic schema provided by the standard story. Our aim is to show that this is a mistake. We shall argue that, once some basic features of motor representations are properly understood, the standard view must be  refined and extended in ways that allow us to recognize distinctive roles for intention and motor representation in explaining the purposiveness of action.

@@

Our overall aim is to show that intention and motor representation play distinctive roles in explaining the purposiveness of action, that is, in relating actions to outcomes to which they are directed. The first temptation standing in our way is the temptation to suppose that motor representation, although perhaps important for action execution in some agents, has no bearing at all on our question about the relation between actions and the outcomes to which they are directed. Just as it would be an error to suppose that details of musculoskeletal structure are relevant to this question, so equally---so the temptation---it would be an error to suppose that facts about motor representation are relevant here.

@@

How does representing an outcome differ from representing merely kinematic or dynamic features of action? How, for instance, does a motor representation of grasping (assuming for now that such a thing exists) differ from a representation of a sequence of joint displacements? First, a motor representation of grasping captures something common to many different sequences of joint displacements and postures involving a variety of effectors. To illustrate, an agent might grasp an object with her hand, with her mouth, with normal pliers (where grasping requires closing the hand), or with reverse pliers (where grasping requires opening the hand). A motor representation of grasping identifies something common to all these cases. Second, and conversely, a motor representation of grasping potentially distinguishes between the same sequence of joint displacements in different contexts. For instance, how a grasping action is represented may depend on a relatively distal outcome: on whether (say) it results in the object grasped being eaten or placed. Also the joint displacements which realise grasping in one context might in another context realise a different action, such as scratching; or they might fail to realise any action at all (because there is no target object, say). Third, a motor representation of an action outcome locates the action within a hierarchical structure. To illustrate, a left-handed precision grip and a right-handed whole hand grip are different action outcomes and both instances of grasping.\footnote{ On the notion of action outcome in motor representation, see \citet{jeannerod_motor_2006} and \citet{rizzolatti_mirrors_2008}.}

@@

Second, motor representations function in monitoring action. They provide inputs to internal predictive models that estimate likely effects of actions. Sensory feedback provides information about the actual course of the action which can be compared against the predictions. Adjustments are made in order to minimise the discrepancy between these \citep{wolpert:1995internal,miall:1996_forward}. Monitoring and control of this kind is a second functional role of motor representation.

@@

So far we have argued that motor processes involve representations of action outcomes. It remains to show that such representations ground purposive actions. But this is hardly a further step. How do intentions ground the purposiveness of actions?  On any standard view, an intention represents an outcome, causes an action, and does so in such a way as to facilitate the outcome's occurrence. Similarly, motor representations of outcomes represent action outcomes, play a role in generating actions, and do this in a way that normally facilitates the occurrence of the outcomes represented. To say that motor representations do all this is one way of making precise the metaphor involved in saying that purposive actions are directed to outcomes.  Moreover, there is a clear resemblance between the natural way of understanding intentions as grounding outcome-directedness and the way in which motor representations ground outcome-directedness.  So given the functional roles and representational objects of motor representations, there is little room for doubt that motor representations can ground the outcome-directedness of purposive actions.

@@

As background we first need a generic distinction between content and format. Imagine you are in an unfamiliar city and are trying to get to the central station. A stranger offers you two routes. Each route could be represented by a distinct line on a paper map. The difference between the two lines is a difference in content. Each of the routes could alternatively have been represented by a distinct series of instructions written on the same piece of paper; these cartographic and propositional representations differ in format. The format of a representation constrains its possible contents. For example, a representation with a cartographic format cannot represent what is represented by sentences such as `There could not be a mountain whose summit is inaccessible.'\footnote{Note that the distinction between content and format is orthogonal to issues about representational medium. The maps in our illustration may be paper map or electronic maps, and the instructions may be spoken, signed or written. This difference is one of medium.} The distinction between content and format is necessary because, as our illustration shows, each can be varied independently of the other.

Our aim in this section is to show that motor representations differ from intentions with respect to their format. This is why the second temptation must be resisted. That motor representations differ in format from intentions shows that they are genuinely distinct phenomena.\footnote{ Readers already convinced that motor representation differs from intention in being non-conceptual will not need the following argument in order to conclude that they are distinct phenomena. However the following considerations also indicate that motor and perceptual representations differ in format, which will be relevant later when we consider how motor representations and intentions jointly lead to action.}

How in general can we identify or distinguish representational formats? Because a representational format is typically associated with characteristic performance profiles, it is sometimes possible to infer similarities and differences in representational format from similarities and differences in the processes in which representations feature. This works both for artefactual and mental representations.  To illustrate in terms of our earlier example, suppose that two people have representations of the same route but for one person the route is represented by a line on a map (so in a cartographic format) whereas the other person has a propositional representation of the route. Some transformations are likely to be easier for the person with the cartographic route representation (depending on the projection used, of course); examples include reversing the route, determining how many times a certain river is crossed and transforming the route into a sequence of compass bearings. Other transformations, such as turning the route into a list of salient landmarks, may be easier for the person with the propositional route description. So some patterns of difference in the two people's performances may be explained by the difference in the formats of their representations. If we did not already know that the two people's route representations involved different formats, we might infer this from the facility with which each performed various transformations of the route.

Cognitive neuroscience frequently depends on inferences of just this type. To illustrate, compare imagining seeing an object moving and with actually seeing it move. For this comparison we need to distinguish two ways of imagining seeing. There is a way of imagining seeing which phenomenologically is something like seeing except that it does not necessarily involve being receptive to stimuli. This way of imagining seeing, sometimes called 'sensory imagining', is commonly distinguished from cognitive ways of imagining seeing which might for example involve thinking about seeing \citep[§2.1]{Gendler:2011_imagination}.%
\footnote{Note that we define sensory imagining in terms of phenomenology and make no stipulations about the processes and representations involved.  This is essential for our purposes, since we wish to consider how evidence bears on a conjecture about the format of representations involved in sensory imagining.}
It is sensorily imagining seeing an object move that we wish to compare with actually seeing an object move.  These two have similarities in characteristic performance profile.  For instance, whether an object can be seen all at once depends on its size and distance from the perceiver; strikingly, when subjects imagine seeing an object, whether they can imagine seeing it all at once depends in the same way on size and distance (\citealp{kosslyn:1978_measuring}; \citealp[p.\ 99ff]{kosslyn:1994_image}.  Also, how long it takes to imagine looking over an object depends on the object's subjective size in the same way that how long it would take to actually look over that object would depend on its subjective size \citep{kosslyn:1978_visual}.%
\footnote{These and further examples are discussed by \citet[p.\ 165]{currie:1997_mental}.} Further, imagining seeing something (for example, imagining seeing a visual mask) can modulate and interfere with actually seeing in much the way that actually seeing the thing imagined would \citep{pearson:2008_functional,ishai:1995_common}. The similarities in characteristic performance profile and the particular patterns of interference are good (if non-decisive) reasons to conjecture that imagining seeing and actually seeing involve representations with a common format.  This conjecture is indirectly supported by evidence that sensorily imagining seeing and actually seeing not only have a common neural basis but also involve similar patterns of cortical activation \citep[e.g.][]{page:2011_erp}.

Let us turn to motor representation. Compare imagining moving a ball with actually moving a ball.  To fully specify the comparison we intend, it is again necessary to distinguish two ways of imagining. One way of imagining action is phenomenologically something like acting except that such imaginings are not necessarily responsive to the features of actual objects and do not necessarily result in bodily movements. To illustrate suppose you are about to dive into a pool and, standing at the edge, mentally pantomime launching yourself from the bank. Some phenomenal characteristics of this imaginative exercise may be barely distinguishable from some of those associated with actually launching yourself into the pool. This way of imagining action can be distinguished from cognitive ways of imagining action which might involve thinking about an action.%
\footnote{
On distinguishing these two ways of imagining action, see \citet[p.\ 161]{currie:1997_mental}, \citet[p.\ 727]{jeannerod:1995_mental}, and \citet[p.\ 638-9]{kosslyn:2001_neural}. The former, phenomenologically action-like imagining is sometimes labelled 'motor' or 'internal' and occasionally identified by its links to motor processes or by features of the format or content of the representations involved (\citealp[p.\ 1400]{annett:1995_motor}). We avoid these labels because we introduce the distinction by appeal to phenomenology only and do not stipulate that motor representations are involved. It is essential for what follows that the involvement of motor representations in the phenomenologically action-like way of imagining action is a discovery rather than a terminological stipulation.}
%
The comparison we intend is between imagining moving a ball in the former, phenomenologically-action like way and actually moving a ball. There is evidence that the way imagining performing an action unfolds in time is similar in some respects to the way actually performing an action of the same type would unfold.  For instance, how long it takes to imagine moving an object is closely related to how long it would take to actually move that object \citep{decety:1989_timing, decety:1996_imagined, Jeannerod:1994oz}. In addition, for actions such as grasping the handle of a cup, manipulating the target object in ways that make the action harder (such as orienting the cup's handle to make it less convenient for you to grasp) make a corresponding difference to the effort involved in imagining performing the action \citep{parsons:1994_temporal, frak:2001_orientation}. Further, imagining performing an action can selectively interfere with performance of a related action. For example, suppose you are faced with an array of objects one of which---the target---you will shortly be required to grasp.  Subjects who imagine grasping an object other than the target object tend to be slower in subsequently grasping the target object than subjects who do not imagine acting or subjects who imagine grasping the target object \citep{ramsey:2010_incongruent_}. Just as the similarities between imagining seeing and actually seeing are evidence for the hypothesis that the representations involved in imagining seeing and actually seeing have a common format, so also the similarities in characteristic performance profile between imagining acting and actually acting, together with the particular patterns of interference between the two, suggest that imagining acting and actually acting involve a common representational format. And much as in the case of seeing and imagining seeing, acting and imagining acting involve many of the same processes almost up to the actual muscle contractions \citep{jeannerod:1995_mental, jeannerod:2003_mechanism}.

The fact that motor representation is involved in one way of imagining acting means that we can use imagining acting to investigate the format of motor representations. This enables us to examine characteristics of processes involving motor representation which are not directly consequences of an agent's actual body or actual environment.

Differences in performance provide reasons to distinguish the formats of visual and motor representations. To see why, consider two tasks involving mental rotation. Judging the laterality of a rotated letter is thought to involve the phenomenologically seeing-like form of imagination \citep{jordan:2001_cortical}, whereas judging the laterality of a rotated hand is thought to involve the phenomenologically action-like form of imagination \citep{parsons:1987_imagined, gentilucci:1998_right}. Ordinary subjects who are asked to judge the laterality of a hand rotated to various degrees are slower and less accurate when the hand's position is maximally biomechanically awkward, when the hand is rotated so that the middle finger points downwards. By contrast, no such effect occurs for comparable tasks involving letters rather than hands. Can this difference in performance in imagining hands and letters be entirely explained by a difference in what is imagined (hands vs. letters)? There are subjects who can perform both tasks but whose performance is not different for hands and letters \citep{Fiori:2012fk}. These are subjects suffering Amyotrophic Lateral Sclerosis (ALS), which impairs motor representation \citep{parsons:1998_cerebrally}. If the hand-letter difference in performance were entirely explained by a difference in what is imagined, we would expect ALS and ordinary subjects to exhibit the same difference in performance since both are imagining hands and letters. But this is not the case. So some differences in performance linked to visual and motor representation cannot be entirely explained by differences in content.  This suggests that the differences in performance are explained by a difference in format.

Given that we need to posit differences in the formats of motor and visual representations in order to explain performance differences in mental rotation, it is plausible that these differences in format also explain some of the differences in performance linked to the timing of, and effort required for, imagining acting and imagining seeing.  For instance, contrast imagining rotating a ball with imagining seeing a ball rotating.%
\footnote{It may be difficult in practice to imagine acting without also imagining seeing, and conversely; it may also sometimes be difficult to distinguish imagine acting from imagining seeing \citep[as][p.\ 170 note]{currie:1997_mental}. However ordinary subjects can separate the two well enough to confirm predictions about their differences \citep[see, e.g.,][]{kosslyn:2001_imagining}.
}
As already mentioned, how quickly the former can be done is a function of how long it would take the agent to rotate the ball, whereas how quickly the latter can be done depends on how rapidly the ball can rotate and still be perceived as rotating. Similarly, we mentioned that factors making actually acting more effortful also make imagining acting more effortful: such factors are unlikely to affect the effort involved in imagining seeing. The explanation for these differences between imagining acting and imagining seeing plausibly involves a difference in the formats of the representations involved. That the two involve different representational formats is consistent with evidence that these two imaginings also involve different processes \citep{kosslyn:2001_imagining}. For instance, each can be selectively impaired \citep{sirigu:2011_motor}; and factors such as limb amputation or hand posture can interfere with imagining acting without interfering with  imagining seeing \citep{nico:2004_left, vargas:2004s_influence,  fourkas:2006_influence}.

So far we have been arguing that motor and visual representations differ in format.  Why suppose that motor representations also differ in format from intentions?  Contrast two ways of imagining taking a shot in basketball, one involving the phenomenologically action-like kind of imagination and the other involving a cognitive kind of imagination.  The contrast we require is roughly between the way a former player might imagine this and the way that someone who has only ever read about basketball might imagine it.  As we have seen, the way the phenomenologically action-like kind of imagination unfolds in time and the amount of effort it involves will depend on bio-mechanical, dynamical and postural constraints, among others. These constraints are closely related to those which govern actually performing such actions \citep{Jeannerod:2001yb}, and some can be altered by acquiring or losing motor expertise.  By contrast no such constraints would be expected always to apply where a cognitive kind of imagination is involved.  In line with the general strategy of inferring differences in format from differences in characteristic performance profile, we conclude that motor representations differ in format from those involved in cognitive kinds of imagination, which are plausibly propositional.

But are we too hasty in concluding that motor and propositional representations differ in format?  It might be objected that their characteristic performance profiles are not so different, for in cognitive imagination the fact that an agent is imagining herself acting will mean that how she imagines the action unfolding will reflect constraints on what she can do. But while this will sometimes be the case, a cognitive kind of imagining need not involve imagining an action unfolding in a way consistent with one's actual abilities. What distinguishes the phenomenologically action-like form of imagination is that some bio-mechanical, dynamical and postural constraints are inescapable.  To make this vivid consider imagining reaching for a distant object.  If the object is manifestly far out of reach it will not normally be possible to do this using the phenomenologically action-like kind of imagination, whereas no such difficulty need occur where a cognitive kind of imagination is involved.  After all, where a cognitive kind of imagination is involved one can imagine having much longer limbs (or an entirely different body) whereas this cannot be achieved at will where the phenomenologically action-like kind of imagination is involved.  Finally, where there are constraints on a cognitive kind of imagination these are generally mediated by beliefs or suppositions about one's own abilities; it seems unlikely that this is true of the phenomenologically action-like kind of imagination.

@@

The interface problem is the problem of explaining how, some of the time, there could be reliable matches between outcomes variously specified by intentions and motor representations. As the previous section explained, the problem arises because intentions and motor representations have different representational formats.

@@

The problem of explaining this we called \emph{the interface problem}. Theoretically uncomplicated approaches to solving it would involve appeal to common causes or to processes of translation. The interface problem is a problem because no such approach is viable given the present state of knowledge. However, we have shown that there is another way of solving the interface problem. This solution hinges on the existence of concepts which refer to actions by deferring to motor representations. Where intentions involve such deferential concepts, their contents are logically linked to those of motor representations and so the interface problem can be solved. In short, then, we have shown that there is a theoretically coherent and empirically plausible solution to the interface problem, one which requires neither common causes nor processes of translation to link intention and motor representation.

>>>>

%\def \papersize {a4paper}
\def \papersize {letterpaper}

@@

\def \ititle {Intention and motor representation in purposive action}
\def \isubtitle {}
\def \iauthor {}
%\def \iauthor {S. Butterfill* \& C. Sinigaglia**
%\\ 
%**Department of Philosophy, University of Warwick
%\\ 
%***Dipartimento di Filosofia, Università degli Studi di Milano}
\def \iemail{s.butterfill@warwick.ac.uk}
%\date{}

\input{$HOME/Documents/submissions/preamble_steve_paper2}
\author{}
\date{}

@@

\begin{abstract}
\noindent
Are there distinct roles for intention and motor representation in explaining the purposiveness of action? Standard accounts of action assign a role to intention but are silent on motor representation. The temptation is to suppose that nothing need be said here because motor representation is either only an enabling condition for purposive action or else merely a variety of intention. This paper provides reasons for resisting that temptation. Some motor representations, like intentions, coordinate actions in virtue of representing outcomes; but, unlike intentions, motor representations cannot feature as premises or conclusions in practical reasoning.  This implies that motor representation has a distinctive role in explaining the purposiveness of action. It also gives rise to a problem: were the roles of intention and motor representation entirely independent, this would impair effective action. It is therefore necessary to explain how intentions interlock with motor representations. The solution, we argue, is to recognise that the contents of intentions can be partially determined by the contents of motor representations. Understanding this content-determining relation enables better understanding how intentions relate to actions.
\end{abstract}

@@

What is the relation between a purposive action and the outcome or outcomes to which it is directed? The standard way of answering this question appeals to intention, a propositional attitude which plays a characteristic role in planning and coordinating action, is linked to practical reasoning and is subject to characteristic norms (\citealp{Bratman:1987xw}).  On the standard view, an action is directed to an outcome in virtue of the action's being appropriately related to an intention which represents this outcome or some related outcome. As this view is usually expounded, the relation between actions and outcomes to which they are directed is treated as largely independent of the motor processes and representations underpinning action execution. Motor representations are usually considered either as philosophically irrelevant enabling conditions, or else as merely filling in additional details of the basic schema provided by the standard story. Our aim is to show that this is a mistake. We shall argue that, once some basic features of motor representations are properly understood, the standard view must be  refined and extended in ways that allow us to recognize distinct roles for intention and motor representation in explaining the purposiveness of action.

@@

Our overall aim is to show that intention and motor representation play distinct roles in explaining the purposiveness of action, that is, in relating actions to outcomes to which they are directed. The first temptation standing in our way is the temptation to suppose that motor representation, although perhaps important for action execution in some agents, has no bearing at all on our question about the relation between actions and the outcomes to which they are directed. Just as it would be an error to suppose that details of musculoskeletal structure are relevant to this question, so equally---so the temptation---it would be an error to suppose that facts about motor representation are relevant here.

@@

How does representing an outcome differ from representing merely kinematic or dynamic features of action? How, for instance, does a motor representation of grasping (assuming for now that such a thing exists) differ from a representation of a sequence of joint displacements? First, a motor representation of grasping captures something common to many different sequences of joint displacements and postures involving a variety of effectors. To illustrate, an agent might grasp an object with her hand, with her mouth, with normal pliers (where grasping requires closing the hand), or with reverse pliers (where grasping requires opening the hand). A motor representation of grasping identifies something common to all these cases. Second, and conversely, a motor representation of grasping potentially distinguishes between the same sequence of joint displacements in different contexts. For instance, how a grasping action is represented may depend on a relatively distal outcome: on whether (say) it results in the object grasped being eaten or placed. Also the joint displacements which realise grasping in one context might in another context realise a different action, such as scratching; or they might fail to realise any action at all (because there is no target object, say). Third, a motor representation of an action outcome locates the action within a hierarchical structure. To illustrate, a left-handed precision grip and a right-handed whole hand grip are different action outcomes and both instances of grasping.\footnote{On the notion of action outcome in motor representation, see \citet{gallese:2000_inner}, \citet{jeannerod_motor_2006} and \citet{rizzolatti_mirrors_2008}.}

@@

Second, motor representations function in monitoring action. They provide inputs to internal predictive models that estimate likely effects of actions. Sensory feedback provides information about the actual course of the action which can be compared against the predictions. Adjustments are made in order to minimise the discrepancy between these \citep{wolpert:1995internal, miall:1996_forward}.

@@

So far we have argued that motor processes involve representations of action outcomes. It remains to show that such representations ground purposive actions. But this is hardly a further step. How do intentions ground the purposiveness of actions?  On any standard view, an intention represents an outcome, causes an action, and does so in a way that would normally facilitate the outcome's occurrence. Similarly, motor representations of outcomes represent action outcomes, play a role in generating actions, and do this in a way that normally facilitates the occurrence of the outcomes represented. To say that motor representations do all this is one way of making precise the metaphor involved in saying that purposive actions are directed to outcomes.  Moreover, there is a clear resemblance between the natural way of understanding intentions as grounding outcome-directedness and the way in which motor representations ground outcome-directedness (as \citealp{pacherie:2008_action}, pp.\ 189-90 has also argued).  So given the functional roles and representational objects of motor representations, there is little room for doubt that motor representations can ground the outcome-directedness of purposive actions.

@@

As background we first need a generic distinction between content and format. Imagine you are in an unfamiliar city and are trying to get to the central station. A stranger offers you two routes. Each route could be represented by a distinct line on a paper map. The difference between the two lines is a difference in content. Each of the routes could alternatively have been represented by a distinct series of instructions written on the same piece of paper; these cartographic and propositional representations differ in format.%
\footnote{Note that the distinction between content and format is orthogonal to issues about representational medium. The maps in our illustration may be paper map or electronic maps, and the instructions may be spoken, signed or written. This difference is one of medium.
} 
The format of a representation constrains its possible contents. For example, a representation with a cartographic format cannot represent what is represented by sentences such as `There could not be a mountain whose summit is inaccessible.'  The distinction between content and format is necessary because, as our illustration shows, each can be varied independently of the other.

Our aim in this section is to show that motor representations differ from intentions with respect to their format. This is why the second temptation should be resisted. That motor representations differ in format from intentions shows that they are genuinely distinct phenomena.\footnote{ Readers already convinced that motor representation differs from intention in being non-conceptual will not need the following argument in order to conclude that they are distinct phenomena. However the following considerations also indicate that motor and perceptual representations differ in format, which will be relevant later when we consider how motor representations and intentions jointly lead to action.}

How in general can we identify or distinguish representational formats? Because representational formats are typically associated with characteristic performance profiles, it is sometimes possible to infer similarities and differences in representational format from similarities and differences in the processes in which representations feature. This works both for artefactual and mental representations.  To illustrate in terms of our earlier example, suppose that two people have representations of the same route but for one person the route is represented by a line on a map (so in a cartographic format) whereas the other person has a propositional representation of the route. Some transformations are likely to be easier for the person with the cartographic route representation (depending on the projection used, of course); examples include reversing the route, determining how many times a certain river is crossed and transforming the route into a sequence of compass bearings. Other transformations, such as turning the route into a list of salient landmarks, may be easier for the person with the propositional route description. So some patterns of difference in the two people's performances may be explained by the difference in the formats of their representations; and some similarities in performance profile may likewise be explained by sameness of format. If we did not already know that the two people's route representations involved different formats, we might infer this from the facility with which each performed various transformations of the route.

Cognitive neuroscience frequently depends on inferences of just this type.
\bf
To illustrate, compare imagining seeing an object moving with actually seeing it move. For this comparison we need to distinguish two ways of imagining seeing. There is a way of imagining seeing which phenomenologically is something like seeing except that it does not necessarily involve being receptive to stimuli. This way of imagining seeing, sometimes called `sensory imagining', is commonly distinguished from cognitive ways of imagining seeing which might for example involve thinking about seeing \citep[§2.1]{Gendler:2011_imagination}.%
\footnote{Note that we define this way of imagining seeing in terms of phenomenology and stipulate nothing about the processes and representations involved.  This is essential for our purposes, since we wish to consider evidence for conjectures about the format of representations it involves.}
It is this way of imagining seeing an object move that we wish to compare with actually seeing an object move.  These two have similarities in characteristic performance profile.  For instance, whether an object can be seen all at once depends on its size and distance from the perceiver; strikingly, when subjects imagine seeing an object, whether they can imagine seeing it all at once depends in the same way on size and distance (\citealp{kosslyn:1978_measuring}; \citealp[p.\ 99ff]{kosslyn:1994_image}).  Also, how long it takes to imagine looking over an object depends on the object's subjective size in the same way that how long it would take to actually look over that object would depend on its subjective size \citep{kosslyn:1978_visual}.%
\footnote{These and further examples are discussed by \citet[p.\ 165]{currie:1997_mental}.
} 
Further, imagining seeing something (for example, imagining seeing a visual mask) can modulate and interfere with actually seeing in much the way that actually seeing the thing imagined would \citep{pearson:2008_functional, ishai:1995_common}. The similarities in characteristic performance profile and the particular patterns of interference are good (if non-decisive) reasons to conjecture that imagining seeing and actually seeing involve representations with a common format. This conjecture is indirectly supported by evidence that imagining seeing and actually seeing not only have a common neural basis but also involve similar patterns of cortical activation \citep[e.g.][]{page:2011_erp}.

Let us turn to motor representation. Compare imagining moving a ball with actually moving a ball.  To fully specify the comparison we intend, it is again necessary to distinguish two ways of imagining. One way of imagining action is phenomenologically something like acting except that such imaginings are not necessarily responsive to the features of actual objects and do not necessarily result in bodily movements. To illustrate suppose you are about to dive into a pool and, standing at the edge, mentally pantomime launching yourself from the bank. In some respects the experiences involved in this imaginative exercise may be barely distinguishable from experiences that might be involved in actually launching yourself into the pool. This way of imagining action can be distinguished from cognitive ways of imagining action which might involve thinking about an action.%
\footnote{
On distinguishing these two ways of imagining action, see \citet[p.\ 161]{currie:1997_mental}, \citet[p.\ 727]{jeannerod:1995_mental}, and \citet[p.\ 638-9]{kosslyn:2001_neural}. The former, phenomenologically action-like imagining is sometimes labelled `motor' or `internal' and occasionally identified by its links to motor processes or by features of the format or content of the representations involved (\citealp[p.\ 1400]{annett:1995_motor}). We avoid these labels because we introduce the distinction by appeal to phenomenology only and do not stipulate that motor representations are involved. It is essential for what follows that the involvement of motor representations in the phenomenologically action-like way of imagining action is a discovery rather than a stipulation.
}
The comparison we intend is between imagining moving a ball in the former, phenomenologically action-like way and actually moving a ball. There is evidence that the way imagining performing an action unfolds in time is similar in some respects to the way actually performing an action of the same type would unfold.  For instance, how long it takes to imagine moving an object is closely related to how long it would take to actually move that object \citep{decety:1989_timing, decety:1996_imagined, Jeannerod:1994oz}. In addition, for actions such as grasping the handle of a cup, manipulating the target object in ways that make the action harder (such as orienting the cup's handle to make it less convenient for you to grasp) make a corresponding difference to the effort involved in imagining performing the action \citep{parsons:1994_temporal, frak:2001_orientation}. Further, imagining performing an action can selectively interfere with performance of a related action. For example, suppose you are faced with an array of objects one of which---the target---you will shortly be required to grasp.  Subjects who imagine grasping an object other than the target object tend to be slower in subsequently grasping the target object than subjects who do not imagine acting or subjects who imagine grasping the target object \citep{ramsey:2010_incongruent_}. Just as the similarities between imagining seeing and actually seeing are evidence for the hypothesis that the representations involved in imagining seeing and actually seeing have a common format, so also the similarities in characteristic performance profile between imagining acting and actually acting, together with the particular patterns of interference between the two, suggest that imagining acting and actually acting involve a common representational format. And much as in the case of seeing and imagining seeing, acting and imagining acting involve many of the same processes almost up to the actual muscle contractions \citep{jeannerod:1995_mental, jeannerod:2003_mechanism}.

We have been comparing actually seeing with imagining seeing and actually acting with imagining acting as a first step towards arguing that visual and motor representations differ in format (which in turn will be background for an argument that motor representation and intention differ in format).  This claim could not easily be established by comparing actually seeing with actually acting because performance differences between these might be explained by bodily or environmental factors only distantly related to the representations involved. By contrast, comparing performance in imagining seeing and imagining acting does provide reasons to conclude that visual and motor representations differ in format. To see why, contrast imagining rotating a ball with imagining seeing a ball rotating.%
\footnote{Imagining acting without also imagining seeing may be difficult in practice, and conversely; it may also sometimes be difficult to distinguish imagining acting from imagining seeing \citep[as][p.\ 170 suggest]{currie:1997_mental}. However ordinary subjects can separate the two well enough to confirm predictions about their differences \citep[see, e.g.,][]{kosslyn:2001_imagining}.
}
As already mentioned, how quickly the former can be done is a function of how long it would take the agent to rotate the ball, whereas how quickly the latter can be done depends on how rapidly the ball can rotate and still be perceived as rotating. Similarly, we mentioned that factors making actually acting more effortful also make imagining acting more effortful. For instance, in some cases rotating a ball clockwise is easier than rotating it anti-clockwise, and so is imagining a ball rotate.  By contrast, the effort involved in actually seeing or imagining seeing a ball rotate does not similarly differ depending on direction.  These and other performance differences are plausibly a consequence of a difference in format between motor and visual representations.

It may be objected that performance differences such as these can be explained without appealing to a difference in format.  After all, rotating a ball involves an action whereas a ball rotating does not; consequently, imagining the former may be thought to differ from imagining the latter with respect to the contents of the representations involved. Supposing that there are differences in content here and in other cases, could these fully explain differences in performance profile?  To see why not, consider two tasks involving mental rotation. Judging the laterality of a rotated letter is thought to involve phenomenologically vision-like imagination \citep{jordan:2001_cortical}, whereas judging the laterality of a rotated hand is thought to involve phenomenologically action-like imagination \citep{parsons:1987_imagined, gentilucci:1998_right}. Ordinary subjects who are asked to judge the laterality of a hand rotated to various degrees are less accurate when the hand's position is biomechanically awkward. By contrast, no such effect occurs for comparable tasks involving letters rather than hands. How could this difference in performance in imagining hands and letters be explained? Consider the claim that the difference in performance can be fully explained by a difference in the content of the representations involved.  Initially this might seem plausible because one task involves hands whereas the other involves letters.  However, there are subjects who can perform both tasks but whose performance is not different for hands and letters \citep{Fiori:2012fk}. These are subjects suffering Amyotrophic Lateral Sclerosis (ALS), which impairs motor representation \citep{parsons:1998_cerebrally}. Since ALS and ordinary subjects encounter the same stimuli and perform the same tasks, there seems to be no reason (other than our hypothesis about a difference in format) to suppose that the two groups' performance involves representations with different contents.  So if the hand-letter difference in performance were entirely explained by a difference in content, we would expect ALS and ordinary subjects to exhibit the same difference in performance. But this is not the case. This is an obstacle to supposing that the hand-letter difference in performance in ordinary subjects could be explained by appeal to content.

The hypothesis that visual and motor representations differ in format is consistent with evidence that imagining acting and imagining seeing involve different processes \citep{kosslyn:2001_imagining}. For instance, each can be selectively impaired \citep{sirigu:2011_motor}; and factors such as limb amputation or hand posture can interfere with imagining acting without interfering with  imagining seeing \citep{nico:2004_left, vargas:2004s_influence,  fourkas:2006_influence}.

So far we have been arguing that motor and visual representations differ in format.  Why suppose that motor representations also differ in format from intentions?  Contrast two ways of imagining taking a shot in basketball, one involving the phenomenologically action-like kind of imagination and the other involving a cognitive kind of imagination.  The contrast we require is roughly between the way a former player might imagine this and the way that someone who has only ever read about basketball might imagine it.  As we have seen, the way phenomenologically action-like imagination unfolds in time and the amount of effort it involves will depend on bio-mechanical, dynamical and postural constraints, among others. These constraints are closely related to those which govern actually performing such actions \citep{Jeannerod:2001yb}, and some can be altered by acquiring or losing motor expertise.  By contrast no such constraints would be expected always to apply where a cognitive kind of imagination is involved.  In line with the general strategy of inferring differences in format from differences in characteristic performance profile, we conclude that motor representations differ in format from those involved in cognitive kinds of imagination, which are plausibly propositional.

But are we too hasty in concluding that motor and propositional representations differ in format?  It might be objected that their characteristic performance profiles are not so different, for in cognitive imagination the fact that an agent is imagining herself acting will mean that how she imagines the action unfolding will reflect constraints on what she can do. But while this will sometimes be the case, a cognitive kind of imagining need not involve imagining an action unfolding in a way consistent with one's actual abilities. What distinguishes the phenomenologically action-like form of imagination is that some bio-mechanical, dynamical and postural constraints are inescapable.  To make this vivid consider imagining reaching for a distant object.  If the object is manifestly far out of reach it will not normally be possible to do this using the phenomenologically action-like kind of imagination, whereas no such difficulty need occur where a cognitive kind of imagination is involved.  After all, where a cognitive kind of imagination is involved one might imagine having much longer limbs (or an entirely different body) whereas this cannot be achieved at will where the phenomenologically action-like kind of imagination is involved.  Finally, where there are constraints on a cognitive kind of imagination these are generally mediated by beliefs or suppositions about one's own abilities; it seems unlikely that this is true of the phenomenologically action-like kind of imagination.

\rm

@@

The interface problem is the problem of explaining how, some of the time, there could be non-accidental matches between outcomes variously specified by intentions and motor representations. As the previous section explained, the problem arises because intentions and motor representations have different representational formats.

@@

The problem of explaining this we called the interface problem. Theoretically uncomplicated approaches to solving it would involve appeal to common causes or to processes of translation. The interface problem is a problem because no such approach is viable given the present state of knowledge. However, we have shown that there is another way of solving the interface problem. This solution hinges on the existence of concepts which refer to actions by deferring to motor representations. Where intentions involve such deferential concepts, their contents are logically linked to those of motor representations and so the interface problem can be solved. In short, then, we have shown that there is a theoretically coherent and empirically plausible solution to the interface problem, one which requires neither common causes nor processes of translation to link intention and motor representation.

A further conjecture is that whenever there is a non-accidental match between the contents of intentions and of motor representations, this is due at least in part to deferential action concepts. The plausibility of this conjecture rests in part on the absence of any other viable full solution to the interface problem, and of course we do not claim to have shown that no alternatives exists. If the conjecture is right, if there is no way of fully solving the interface problem other than by means of deferential action concepts, then concepts which refer by deferring to motor representations are what tie explicit practical reasoning to motor processes.
